\documentclass[11pt,a4paper,sans]{moderncv}
\moderncvstyle{banking}
\moderncvcolor{black}
\nopagenumbers{}
\usepackage[utf8]{inputenc}
\usepackage{ragged2e}
\usepackage[scale=0.915]{geometry}
\usepackage{import}
\usepackage{multicol}
\usepackage{import}
\usepackage{enumitem}
\usepackage[utf8]{inputenc}
\usepackage{amssymb}
\name{Martin Augusto}{Ippolito}
\newcommand*{\customcventry}[7][.13em]{
\begin{tabular}{@{}l}
{\bfseries #4} \
{\itshape #3}
\end{tabular}
\hfill
\begin{tabular}{l@{}}
{\bfseries #5} \
{\itshape #2}
\end{tabular}
\ifx&#7&%
\else{\
\begin{minipage}{\maincolumnwidth}%
\small#7%
\end{minipage}}\fi%
\par\addvspace{#1}}
\begin{document}
\makecvtitle
\vspace*{-16mm}
\begin{center}\textbf{ Full-Stack Developer}\end{center}
\begin{center}
\begin{tabular}{ c c c }
\faMobile\enspace +54 9 11 4141-4579 & \enspace martinippo@gmail.com & \faHome\enspace Buenos Aires, Argentina \\
\faLinkedin\enspace \color{blue} \href{https://www.linkedin.com/in/martin-ippolito/}{in/martin-ippolito/} &
\faGithub\enspace \color{blue} \href{https://github.com/martinippo01}{github.com/martinippo01} & \enspace {\faGlobe\enspace \color{blue} \href{https://www.ippo.com.ar}{ippo.com.ar}
\end{tabular}
\end{center}

% \section{Profile}
% {Innovative Digital Marketing Manager with 5+ years of experience managing online marketing campaigns and leading cross-functional teams. Skilled in developing integrated marketing strategies that drive brand awareness, engagement, and conversions. Regularly exceed performance targets and possess advanced analytical and problem solving skills. Adept at leveraging cutting-edge digital tools and platforms to achieve marketing objectives.}

\section{Profile}
\justify
Dynamic Full-Stack Developer with a passion for creating innovative solutions and leveraging technology to drive business success. Possessing a solid foundation in software engineering with a focus on web development, database management, and object-oriented programming. Equipped with years of experience both in Argentina and the United Kingdom. My expirience includes various roles, such as Software development, teaching programming, leading teams, and assisting in educational activities. Furthermore, developed several personal projects individually and in teams. 

\section{Areas of Expertise}
{Front end Frameworks - Data bases (SQL and NoSQL) - OOP programming (Java and Python) - Team Leader - Teaching - Low level programming (C)}

\section{Professional Experience}
\customcventry{05/2024 ‐ present}{{\color{blue}\href{https://wuru.ai/}{(Wúru)}}}{Frontend developer,}{Buenos Aires, ARG}{}{
{\begin{itemize}[leftmargin=0.6cm, label={\textbullet}]
\item Javascript with Svelte Framework, Python with FastAPI
\end{itemize}}}

\customcventry{03/2022 ‐ present}{{\color{blue}\href{https://lasalleflorida.edu.ar/}{(La Salle Florida Technical School)}}}{Programming and networking teacher,}{Buenos Aires, ARG}{}{
{\begin{itemize}[leftmargin=0.6cm, label={\textbullet}]
\item Teaching advanced C programming, Networking protocolos and Web Development
\end{itemize}}}

\customcventry{10/2021 ‐ 08/2022}{{\color{blue}\href{https://www.sabf.org.ar/}{(South American Business Forum)}}}{Head of Media And Communication,}{Buenos Aires, ARG}{}{
{\begin{itemize}[leftmargin=0.6cm, label={\textbullet}]
\item Leader of a team of four.
\item Responsible for the conference's image, graphic material and social media.
\end{itemize}}}


\customcventry{Summer 2019}{{\color{blue}\href{https://www.millfieldenterprises.com/melhc}{(Millfield School)}}}{Activity Assistant,}{Somerset, UK}{}{
{\begin{itemize}[leftmargin=0.6cm, label={\textbullet}]
\item Responsible for groups of teenagers at the Millfield English Language Holiday Courses.
\item Worked on campus
\end{itemize}}}


% \section{Online Courses \& Certifications}
% {\begin{itemize}[label=\textbullet]
%       \item Introduction to Digital Marketing (Jan. 2023) - \underline{\color{blue}\href{https://google.com/}{SEMRUSH}}
%       \item Career Essentials in Digital Marketing by LinkedIn (Aug. 2022) - \underline{\color{blue}\href{https://google.com/}{LinkedIn}}
%       \item Visualization with Tableau (Feb. 2022) - \underline{\color{blue}\href{https://google.com/}{Coursera}}
%       \item Foundations of Google Analytics  (Jun. 2021) - \underline{\color{blue}\href{https://google.com/}{Google, Coursera}}
%      \item Google Analytics for Power Users (Jun. 2021) - \underline{\color{blue}\href{https://google.com/}{Google}}
%        \item The Fundamentals of Digital Marketing, (Jul. 2019) - \underline{\color{blue}\href{https://google.com/}{Google}} 
%   \end{itemize}} 

\section{Education}
\customcventry{2020-2025}{\color{blue}\href{https://www.itba.edu.ar/}{Instituto Tecnológico de Buenos Aires}}{Software Engineer}{Buenos Aires, ARG}{}{}{}

% \customcventry{2013-2019}{\color{blue}\href{https://lasalleflorida.edu.ar/}{Instituto La Salle Florida}}{Electronic Technician}{Buenos Aires, ARG}{}{}{}

\section{Projects}
See full list of projects at: {\color{blue} \href{https://www.ippo.com.ar/\#projects}{ippo.com.ar/\#projects}}


\section{Skills}
{\begin{itemize}[label=\textbullet]
\item {\textbf{OOP languages:} Python, Java, Ruby}
\item {\textbf{SQL:} PostgreSQL, MySQL}
\item {\textbf{NoSQL:} MongoDB, Cassandra, neo4j, Redis}
\item {\textbf{Front-End frameworks:} React, Next.JS, Vue.JS, Ionic framework, Svelte}
\item {\textbf{Low level programming:} C}
\end{itemize}}

\section{Languages}
\begin{multicols}{2}
    \begin{itemize}[label=\textbullet]
    \item \textbf{English} [Native]
    \item {\textbf{Spanish} [Native]}

    \end{itemize}
\end{multicols}
\end{document}
